Marlowe: financial contracts on blockchain

### 2018-05-17 tex/paper.tex
changes to section 2.1

The DSL is modelled as an algebraic type in Haskell, together with an executable small-step semantics. 
We start by looking at the different types used by the model, then we look at the \haskellinline{Contract} DSL itself, 
and finally we give its semantics in Haskell. Section \ref{section:example-saving} gives an example of Marlowe in 
action, and Section
\ref{section:example-escrow} shows the advantage of seeing Marlowe as a DSL embedded in Haskell.

@@

First, it will need to observe different kinds of varying quantities including, for example, the current time, the 
current block number and, random numbers, as well as ``real world'' quantities like ``the price of oil'' or ``the 
exchange rate between currencies A and B''. Each instance of such an observable will be recorded on the blockchain to 
allow the computation to be repeated for verification purposes. It is assumed that at each step of the execution of the 
contract, the values of some observables will be needed, and these values are (together) given by a value of type 
\haskellinline{OS}. Note that these values are not determined by the participants in the contract, but rather by the 
external environment.

As the examples illustrate, observables come both from aspects of the blockchain (e.g.\ current block number) and 
externally. In the latter case it will be necessary to agree a trusted oracle or beacon giving the value, which can then 
be stored (or a hash stored) on chain.

\paragraph{Inputs}

On the other hand, at each step there are -- potentially, at least -- a variety of inputs available from the 
participants. These include commitments of currency (or ``cash''), redemption of commitments, and claims of payments by 
a participant; moreover it is also possible for a participant to input an arbitrary value (which we term a ``choice''). 
The particular inputs at a given step are described by a value of type \haskellinline{Input}.

\paragraph{Commitments}

While informally we might see a commitment to something as being indefinite, it is important to realise that on 
blockchain a commitment needs to have a timeout so that progress can be forced in a game. After the timeout period the 
cash can be refunded through the user creating a transaction to reclaim the cash.
Information about the commitments currently in force forms the \haskellinline{State}, which is (potentially) modified 
at each execution step.

@@

\paragraph{The \haskellinline{step} function}

This analysis justifies the type of the \haskellinline{step} function:

@@

\begin{itemize}
\item It is assumed that cryptographic functions and operations are provided by a layer external to the system, and so 
they need not be modelled explicitly here.
\item We assume that time is ``coarse grained'' and measured simply by block number, so that timeouts etc.\ are 
delimited using nothing finer than block number. 
\item Because we assume a ``pull'' model, making a commitment is not something that a contract can perform; rather, it 
can enable that a commitment is made, but that then has to be established externally: hence the input of (a set of) 
commitments at each step. The same observation also applies to redeeming a commitment of cash. Commitments that have 
been made or redeemed need to be recorded somehow.

\item Observables are observed at a particular time and in a particular context. We assume that the recording and 
identification of each (instance of an) observation is provided by the infrastructure of the system. We provide a 
``little language'' for describing observations: \haskellinline{Observation}. 
\item
Similar properties are true for
\haskellinline{Money} amounts: their values are calculated depending on the inputs and state of execution of the 
contract, they can be deterministically established given the context, and they are described through a small 
``expression language''.
\item It is important to be aware that there may be different instances of contracts executed, and for each instance 
there will typically be different instances of observables (and commitments) observed and recorded.
\item The model manages the release of funds back to the committer when a cash commitment expires (see discussion of 
the \haskellinline{stepBlock} function below).
\end{itemize}

@@

>>>>

The DSL is modelled as an algebraic type in Haskell, together with an executable small-step semantics. 
We start by looking at the different types used by the model, and the assumptions about the infrastructure in which contracts will be run. We then we look at the \haskellinline{Contract} DSL itself, 
and finally we give its semantics in Haskell. Section 
%\ref{section:example-saving} gives an example of Marlowe in action, and Section
\ref{section:example-escrow} revisits the ``escrow'' example using the embedding of Marlowe as a DSL in Haskell.

@@

First, it will need to observe different kinds of varying quantities including, for example, the current time, the 
current block number and, random numbers, as well as ``real world'' quantities like ``the price of oil'' or ``the 
exchange rate between currencies A and B''. 
As the examples illustrate, observables come both from aspects of the blockchain (e.g.\ the current block number) and 
externally. In the latter case it will be necessary to agree a trusted oracle or beacon giving the value.

Each instance of such an observable will be observed at a particular time and in a particular context. We assume that the system infrastructure ensures that these values are recorded on the blockchain to 
allow the computation to be repeated for verification purposes.

It is assumed that at each step of the execution of the 
contract, the values of observables will be available if needed, and these values are (together) given by a value of type 
\haskellinline{OS} (for ``observable set''), where individual observations are described in a 
``little language'' for that purpose: \haskellinline{Observation}. 
Note that these values are not determined by the participants in the contract, but rather by the 
external environment in which the contract is run.

\paragraph{Inputs and Commitments}

On the other hand, at each step there are -- potentially, at least -- a variety of inputs available from the 
participants themsleves. These include commitments of currency (or ``cash''), redemption of commitments, and claims of payments by 
a participant. <oreover it is also possible for a participant to input an arbitrary value (which we term a ``choice''). 
The particular inputs at a given step are described by a value of type \haskellinline{Input}.

%\paragraph{Commitments}

While informally we might see a commitment to something as being indefinite, it is important to realise that on 
blockchain a commitment needs to have a timeout so that progress can be forced in a contract. After the timeout period the 
cash can be refunded through the user creating a transaction to reclaim the cash.
Information about the commitments currently in force forms the \haskellinline{State}, which can be  modified 
at each execution step.

\paragraph{Actions}

@@

@@

\begin{itemize}
\item It is assumed that cryptographic functions and operations are provided by a layer external to the system, and so 
they need not be modelled explicitly.
\item We assume that time is ``coarse grained'' and measured by block number, so that in particular timeouts are 
delimited using block numbers. 
\item 
Making a commitment is not something that a contract can perform; rather, it 
can request that a commitment is made, but that then has to be established externally: hence the input of (a set of) 
commitments at each step.
\item
IS THIS NEEDED???
Amounts of \haskellinline{Money} amounts can be calculated depending on the inputs and state of execution of the 
contract. They can be deterministically established given the context, and they are described through a small 
``expression language''.
\item The model manages the release of funds back to the committer when a cash commitment expires (see discussion of 
the \haskellinline{stepBlock} function below).
\end{itemize}

@@

The \haskellinline{step} function represents a \emph{single computation step} and has this type:
